### 2022-12-22 sections/experiments/_synthetic.qmd
rejigged artifacts

```{julia}
max_obs = 1000
catalogue = load_synthetic(max_obs; data_dir=data_path)
choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
data_sets = filter(p -> p[1] in choices, catalogue)
```

@@

>>>>

```{julia}
max_obs = 1000
catalogue = load_synthetic(max_obs)
choices = [
    :linearly_separable, 
    :overlapping, 
    :circles, 
    :moons,
]
data_sets = filter(p -> p[1] in choices, catalogue)
```

@@

```{julia}
generate_artifacts(output_path)
generate_artifacts(www_path)
```
